Retrofitting Effect Handlers onto OCaml

### 2021-03-14 retro-concurrency.tex
space
edits

\author{Anil Madhavapeddy}
\affiliation{
  \institution{\small University of Cambridge Computer Laboratory and OCaml Labs}            %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{avsm2@cl.cam.ac.uk}          %% \email is recommended

@@

\subsection{Asynchronous I/O}
\label{sec:aio}

@@

\begin{lstlisting}
let rec spawn f =
  match f () with
	...
  | effect (Read ic) k -> continue k (input_line ic)
\end{lstlisting}
%
which uses OCaml standard library's |input_line| function to read a line from
the channel |ic| and resume the continuation |k| with the resultant string.
However, performing reads synchronously blocks the entire scheduler, preventing
other threads to run until the I/O is completed.

>>>>

\author{Anil Madhavapeddy}
\affiliation{
  \institution{\small University of Cambridge and OCaml Labs}            %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{avsm2@cl.cam.ac.uk}          %% \email is recommended

@@

\vspace{-1em}
\subsection{Asynchronous I/O}
\label{sec:aio}

@@

\begin{lstlisting}
let rec spawn f =
  match f () with
	...
  | effect (Read ic) k -> continue k (input_line ic)
\end{lstlisting}
%
This uses OCaml standard library's |input_line| function to read a line from
the channel |ic| and resume the continuation |k| with the resultant string.
However, performing reads synchronously blocks the entire scheduler, preventing
other threads from running until the I/O is completed.
